Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 13:12

---
title: Long term cloud enhancement events of global solar irradiance over Thessaloniki

@@

# Intro

The shortwave solar irradiance, reaching Earth's surface, is the main energy source
of the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
has direct practical application, in industries like energy and
agricultural production. The variability of its intensity, can cause difficulties in
predicting the yield, and designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability is the interaction of GHI with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can enhance
the total shortwave irradiance reaching the ground. This effect, can locally increase
the observed GHI, even higher than the expected clear sky irradiance
[see references therein].

>>>>

---
title: Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

@@

# Introduction

The shortwave solar radiation, reaching Earth's surface, is the main energy source of
the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
has direct practical application; in industries like energy and agricultural
production. The variability of its intensity; can impose difficulties in predicting
the yield; and in designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the renewable energy
production in a fine timescale and in near real-time (for a review see @Inman2013;
@Graabak2016).

An important aspect of the variability of solar radiation is its interaction with the
clouds. In general, clouds can attenuate a fraction  of solar irradiance, but under
certain conditions, can lead to  enhancement of the global horizontal irradiance
(GHI) reaching the ground. This effect can locally increase the observed GHI to
levels even higher than the expected clear-sky irradiance [@Cordero2023; @Vamvakas2020 see references therein].
